Approximation as Differentiation notes

### 2025-02-24 notes/definitions.tex
Define 'zero object'.

$\CMon$ is symmetric closed monoidal, with the trivial one-element monoid $\One$ as terminal object and
monoidal product $A \tensor B$ given by the direct product of $A$ and $B$. $\CMon$ is complete and cocomplete,
inheriting all limits and colimits from $\Set$.

@@

Suppose $C$ a $\CMon$-enriched category. For any objects $A, B$, the \emph{biproduct} of $A$ and $B$ is an
object $A \oplus B$ of $C$ together with morphisms

@@

\begin{salign*}
i_A \comp p_A + i_B \comp p_B &= \id_{A \oplus B}
\end{salign*}

@@

\begin{proposition}
\item
\begin{itemize}
\item If $C$ has products (or coproducts), then they are biproducts and thus $C$ is semi-additive.
\item If $C$ has a terminal (or initial) object then it is both initial and terminal.
\end{itemize}
\end{proposition}

>>>>

$\CMon$ is symmetric closed monoidal, with the trivial one-element monoid $\One$ as terminal object, monoidal
product $A \tensor B$ given by the direct product of $A$ and $B$, and braiding given by the isomorphism $A
\times B \iso B \times A$. $\CMon$ is complete and cocomplete, inheriting all limits and colimits from $\Set$.

@@

\begin{definition}[Zero object]
A \emph{zero} object is an object which is both terminal and initial.
\end{definition}

Suppose $C$ a $\CMon$-enriched category.

\begin{definition}[Biproduct]
For any objects $A, B$, the \emph{biproduct} of $A$ and $B$ is an object $A \oplus B$ of $C$ together with
morphisms

@@

\begin{salign*}
i_A \comp p_A + i_B \comp p_B &= \id_{A \oplus B}
\end{salign*}
\end{definition}

@@

\begin{proposition}
\item
\begin{itemize}
\item If $C$ has products (or coproducts) then they are biproducts.
\item If $C$ has a terminal (or initial) object then it is a zero object.
\end{itemize}
\end{proposition}

\noindent We say that $C$ is \emph{semi-additive} if it has finite biproducts.
